Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-14 paper.tex
removed old todonote
edits to conclusions

For a direct comparison, a relative error norm of a quantity $X_{ij}$ over all states $j$ and reactions (or species) $i$ was computed using the $L^{\infty}$ norm:
\begin{equation}
E_{X} = \left\lVert \frac{\left\lvert X_{ij,\text{CT}} - X_{ij}\right\rvert}{\num{e-10} + \num{e-6} \times \left\lvert X_{ij,\text{CT}} \right\rvert} \right\rVert_{\infty} \;,
\label{e:rel_err}
\end{equation}
where the \text{CT} subscript indicates values from Cantera~\cite{Cantera}.
\todo[inline]{the $i,j$ subscript for the overall norm looks a little strange to me, is that typical?}

@@

In this work, we developed automatically generated OpenCL codes for SIMD and SIMT-vectorized evaluations of thermochemical source-term and sparse\slash dense chemical kinetic Jacobian matrices.
\revise{The main contributions of this work are:}
\begin{itemize}
 \item \revise{the derivation and validation of a new Jacobian formulation for \texttt{pyJac} that greatly increases sparsity.}
 \item \revise{the extension of \texttt{pyJac} to enable vectorized execution on the CPU, GPU and other accelerators}
 \item \revise{achievement of significant speedups over a strictly parallel Jacobian and source-term evaluation on SIMD-enabled processors (e.g., CPUs)}
\end{itemize}

\revise{The new formulation for \texttt{pyJac}, including both constant-volume and constant-pressure assumptions, resulted in highly sparse chemical kinetic Jacobians.}
\revise{Though the Jacobian approximation discussed in~\cref{S:sparsity} is not a key feature of this work, future efforts to develop more sophisticated Jacobian approximations would be a worthwhile endevour.}

>>>>

For a direct comparison, a relative error norm of a quantity $X_{ij}$ over all states $j$ and reactions (or species) $i$ was computed using the $L^{\infty}$ norm:
\begin{equation}
E_{X} = \left\lVert \frac{\left\lvert X_{ij,\text{CT}} - X_{ij}\right\rvert}{\num{e-10} + \num{e-6} \times \left\lvert X_{ij,\text{CT}} \right\rvert} \right\rVert_{\infty} \;,
\label{e:rel_err}
\end{equation}
where the \text{CT} subscript indicates values from Cantera~\cite{Cantera}.

@@

In this work, we developed automatically generated OpenCL codes for SIMD and SIMT-vectorized evaluations of thermochemical source-term and sparse\slash dense chemical kinetic Jacobian matrices.
\revise{The main contributions of this work are:}
\begin{itemize}
 \item \revise{Deriving and verifying a new Jacobian formulation for \texttt{pyJac} that greatly increases sparsity;}
 \item \revise{Extending \texttt{pyJac} to enable vectorized execution on the CPU, GPU, and other accelerators; and}
 \item \revise{Achieving significant speedups over a strictly parallel Jacobian and source-term evaluation on SIMD-enabled processors (e.g., CPUs).}
\end{itemize}

\revise{The new formulation for \texttt{pyJac}, including both constant-volume and constant-pressure assumptions, resulted in highly sparse chemical kinetic Jacobians.
Though the Jacobian approximation discussed in~\cref{S:sparsity} is not a key feature of this work, future efforts to develop more sophisticated Jacobian approximations would be a worthwhile endevour.}
